Weekly group meetings

### 2023-06-05 diapo/groupTemplate/main.tex
Almost completed the new template, needs theme now

@@

\begin{frame}
  \frametitle{}
\end{frame}

>>>>

\usepackage{tikz}
%\input{shape.tex}

@@

\begin{frame}{What's new}
  \begin{itemize}
    \item Results obtianed :
      \begin{itemize}
          \color{text}
        \item
      \end{itemize}
    \item Improvements :
      \begin{itemize}
          \color{text}
        \item
      \end{itemize}
    \item Relevant information :
      \begin{itemize}
          \color{text}
        \item test
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Problems/doubts}
  \begin{itemize}
    \item Things that must me sorted out in order to continue with your work.\\ Explain the problem.
    \item Things that you do not understand.
  \end{itemize}
\end{frame}

\begin{frame}{Next weeks}

  List of what I plan to do in the next weeks :

  \centering
  \rowcolors{2}{evenRow}{oddRow}
  \begin{tabular}{ c m{4cm} }
    \rowcolor{firstRow}
    & \centering\color{white}Task \cr
    1 & test23 \\
    2 & test23 \\
    3 & test23 \\
    4 & test23 \\
    5 & test23 \\
  \end{tabular}
\end{frame}

\begin{frame}{Networking and sharing}

  \begin{tikzpicture}
    \node (rect) at (0,0) [rounded corners,draw=text,very thick,minimum width=5.7cm,minimum height=6cm] {Help/collaboration};
    \node (rect) at (6.2,0) [rounded corners,draw=text,very thick,minimum width=5.7cm,minimum height=6cm] {\raggedleft autre chose };
  \end{tikzpicture}
\end{frame}
